### 2025-09-22 src/articles/article6.qmd
Fix glossary

1. Two signatures are required on all accounts of the chapter, pursuant to the International Bylaws (IBL), Article V, Section 9, paragraph b.
1. Neither the chapter nor alumni corporation can have or use any form of ATM, debit, credit or money card that is attached to any account of the chapter or alumni corporation.
1. An officer cannot issue a check to himself.
1. All transactions made by the chapter will not utilize a petty-cash system and must be made by check. All transactions made to the chapter will not utilize a petty-cash system for payments exceeding $100.
1. All reimbursements require a receipt.
1. All statements and record books are reconciled monthly.
1. Only the President or Treasurer may sign contracts on behalf of the chapter.

@@

1. The Treasurer will present a preliminary budget to the Budget Committee (Article V, Section G, Item 2c) no later than six weeks before the beginning of the Fall Semester.
1. The Treasurer will submit the final budget proposal, as approved by the Budget Committee, for the following academic year to the chapter no later than three weeks before the beginning of the Fall Semester. The proposal must be approved by a supermajority vote of the chapter.
   a. Following approval by the chapter, the budget proposal will be presented to the Alumni Corporation and the Alumni Financial Advisor.
1. Budget Committee
   a. The Budget Committee (Article V, Section G, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
   a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
1. Any officer with a budget may distribute portions of their budget as they see fit. 5. Safety Margin and Emergency Fund
   a. Any money leftover for the year from the Safety Margin must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved. This account is only to be accessed with the vote of Executive Council (EC) and the Chapter Advisory Board (CAB).

@@

1. Each brother, New Member, and Alumnus is responsible for any fraternity property damaged, broken, or lost due to any negligence or carelessness on the part of that person or their guest.
   a. Any decision regarding this rule will be decided by EC.
1. Brothers will pay all dues and other financial obligations to the chapter as defined in the budget.
1. Brothers may send a notice directly to the president that they will not be paying dues for the coming semester. One month after this notice has been sent, the brother is automatically suspended.

@@

1. If a brother deems that they will be unable to pay their bill by the due date, they may submit a request for deferment.
1. A request for deferment must be submitted to EC by the due date of the bill that is being deferred.
1. A deferment must be approved by a vote of EC or a supermajority vote of the chapter.
1. A brother that is not following the payment plan in their deferment will have their account balance considered past due.
1. Interest on late payments may be charged at the discretion of EC.

@@

1. The chapter may, by unanimous ballot, exempt a brother from payment of any debts owed to the chapter.
   a. The unpaid debt will be divided equally among the other members of the chapter.

1. If the account balance of any brother, New Member, or Alumnus is negative and past due, he will be placed on financial probation unless a deferment has been approved.
   a. A brother placed on financial probation will be fined no more than $20.
   a. A brother on financial probation loses voting rights.
   a. If a brother is on financial probation for more than one week, a suspension trial will be scheduled for him.
   a. The Alumni Corporation and the chapter financial advisor will be notified of any brother placed on financial probation.

1. If a brother has a debt, including deferments, of over $3,000:
   a. EC will vote on whether or not to hold a suspension trial for him after every bill.
   a. The Treasurer will announce the brother's status to the chapter after every bill.
   a. Any receipt forms that the brother submits must be credited against the debt unless EC approves an exception.

@@

1. EC and CAB will have access to all accounts, including bank accounts, budgeting and financial software, the current ledger, and Greek Bill (or whatever online service is currently being used).

@@

   a. The chair who controls the budget in question.
      i. If the budget is not under a particular chair, or the chair is indisposed, the president may act as a substitute.
      i. If the chair who controls the budget is also the treasurer, any other member of EC may act as a substitute.

   a. Any other non-treasurer member of EC.

>>>>

1. Two signatures are required on all accounts of the chapter, pursuant to the International Bylaws ({{< var acronyms.ibl >}}), Article V, Section 9, paragraph b.
1. Neither the chapter nor alumni corporation can have or use any form of ATM, debit, credit or money card that is attached to any account of the chapter or alumni corporation.
1. An officer cannot issue a check to himself.
1. All transactions made by the chapter will not utilize a petty-cash system and must be made by check. All transactions made to the chapter will not utilize a petty-cash system for payments exceeding $100.
1. All reimbursements require a receipt.
1. All statements and record books are reconciled monthly.
1. Only the President or Treasurer may sign contracts on behalf of the chapter.

@@

1. The Treasurer will present a preliminary budget to the Budget Committee (Article V, Section G, Item 2c) no later than six weeks before the beginning of the Fall Semester.
1. The Treasurer will submit the final budget proposal, as approved by the Budget Committee, for the following academic year to the chapter no later than three weeks before the beginning of the Fall Semester. The proposal must be approved by a {{< var glossary.supermajority >}} vote of the chapter.
   a. Following approval by the chapter, the budget proposal will be presented to the Alumni Corporation and the Alumni Financial Advisor.
1. Budget Committee
   a. The Budget Committee (Article V, Section G, Item 2c) will be created and convened no later than six weeks before the beginning of the Fall semester.
   a. The committee will create a budget to be submitted to the chapter based on the preliminary budget created by the Treasurer.
1. Any officer with a budget may distribute portions of their budget as they see fit. 5. {{< var glossary.safety-margin >}} and Emergency Fund
   a. Any money leftover for the year from the {{< var glossary.safety-margin >}} must be moved to an emergency fund account until that account has 50% of the next year's projected expenses saved. This account is only to be accessed with the vote of Executive Council ({{< var acronyms.ec >}}) and the Chapter Advisory Board ({{< var acronyms.cab >}}).

@@

1. Each brother, New Member, and Alumnus is {{< var glossary.responsible >}} for any fraternity property damaged, broken, or lost due to any negligence or carelessness on the part of that person or their guest.
   a. Any decision regarding this rule will be decided by {{< var acronyms.ec >}}.
1. Brothers will pay all dues and other financial obligations to the chapter as defined in the budget.
1. Brothers may send a notice directly to the president that they will not be paying dues for the coming semester. One month after this notice has been sent, the brother is automatically suspended.

@@

1. If a brother deems that they will be unable to pay their bill by the due date, they may submit a request for {{< var glossary.deferment >}}.
1. A request for {{< var glossary.deferment >}} must be submitted to {{< var acronyms.ec >}} by the due date of the bill that is being deferred.
1. A {{< var glossary.deferment >}} must be approved by a vote of {{< var acronyms.ec >}} or a {{< var glossary.supermajority >}} vote of the chapter.
1. A brother that is not following the payment plan in their {{< var glossary.deferment >}} will have their account balance considered past due.
1. Interest on late payments may be charged at the discretion of {{< var acronyms.ec >}}.

@@

1. The chapter may, by unanimous {{< var glossary.ballot >}}, exempt a brother from payment of any debts owed to the chapter.
   a. The unpaid debt will be divided equally among the other members of the chapter.

1. If the account balance of any brother, New Member, or Alumnus is negative and past due, he will be placed on {{< var glossary.financial-probation >}} unless a {{< var glossary.deferment >}} has been approved.
   a. A brother placed on {{< var glossary.financial-probation >}} will be fined no more than $20.
   a. A brother on {{< var glossary.financial-probation >}} loses voting rights.
   a. If a brother is on {{< var glossary.financial-probation >}} for more than one week, a suspension trial will be scheduled for him.
   a. The Alumni Corporation and the chapter financial advisor will be notified of any brother placed on {{< var glossary.financial-probation >}}.

1. If a brother has a debt, including {{< var glossary.deferment >}}s, of over $3,000:
   a. {{< var acronyms.ec >}} will vote on whether or not to hold a suspension trial for him after every bill.
   a. The Treasurer will announce the brother's status to the chapter after every bill.
   a. Any receipt forms that the brother submits must be credited against the debt unless {{< var acronyms.ec >}} approves an exception.

@@

1. {{< var acronyms.ec >}} and {{< var acronyms.cab >}} will have access to all accounts, including bank accounts, budgeting and financial software, the current ledger, and Greek Bill (or whatever online service is currently being used).

@@

   a. The chair who controls the budget in question.
      i. If the budget is not under a particular chair, or the chair is indisposed, the president may act as a substitute.
      i. If the chair who controls the budget is also the treasurer, any other member of {{< var acronyms.ec >}} may act as a substitute.

   a. Any other non-treasurer member of {{< var acronyms.ec >}}.

### 2025-09-22 src/articles/article7.qmd
Fix glossary

1. No alcohol is to be consumed in the house or on the chapter property.
1. No alcohol is to be stored in the house or on the chapter property except for the purposes of cooking.
   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a simple majority vote of chapter, may only be stored for a period of twenty-four hours.
   a. Alcohol manufactured for the sole sake of cooking (i.e. modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in Article VII, Section A, Item 2a, may be stored indefinitely.
1. Tobacco may not be possessed and chewed within the house or on the chapter property.
1. Illegal substances may not be possessed, stored, or used in the house or on the chapter property.
1. If a brother or their guest violates Article VII, Section A, Item 1, Article VII, Section A, Item 2, Article VII, Section A, Item 3, or Article VII, Section A, Item 4, they will be brought up for standards by the President, with sanctions not less than:
   a. First Offense – $50 fine
   a. Second Offense – $75 fine, placed on probation, and becomes staggard
   a. Third Offense – $100 fine and recommendation for suspension to the chapter
1. No candles will be burned inside the house or on the chapter property.
1. Article VII, Section A, Item 1, Article VII, Section A, Item 2, and Article VII, Section A, Item 3 will become null and void upon the downfall of Western Civilization.

@@

1. All active brothers are to live in the chapter house pursuant to Article V, Section 10 of the International Bylaws (IBL).
   a. The following brothers are exempt from this policy:
      i. 1st year students
      i. Commuter Students
      i. Those who are married
      i. Those who receive housing as compensation for employment (e.g. Resident Assistants)
      i. Those who are on Co-op, Study Abroad, or a similar program
      i. Those who were ineligible or exempt at the beginning of the school year\
      i. Those with a prohibitive medical condition as approved by Case Western Reserve University (CWRU)

@@

1. In order for a brother to move into the house, they must not be on financial probation and must not have a debt to the chapter exceeding $3000, including deferments.
   a. Brothers living in the house during the fall of any year are exempt from this stipulation for the spring semester of that year only.

@@

1. Alumni will be permitted one year after graduation or status change to live in the house without chapter approval. After that semester, the brother in question must receive a supermajority vote in order to remain in the house.
   a. Alumni must be taking classes at CWRU to live in the house (i.e. as a graduate student).

1. Only a spouse to a brother living in the house and taking classes at CWRU may live in the house during the school year. A spouse meeting the qualifications must receive a supermajority vote of the chapter to live in the house.

@@

   a. Brothers who have lived in the house during the school year for at least one semester will be allowed the option of moving out in order of pledge class from oldest to most recent, at the discretion of the Vice President.
      i. The house may not be dropped below capacity.
      i. If this method would bring the house below capacity:\
         1\. Of the brothers with the highest roster number among those who wish to move out, select the number of brothers that would bring the house to a mutually acceptable method.

   a. If, after application of the method described in Article VII, Section C, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified roster number will be forced to move out first.
      i. Brothers listed in Article VII, Section B, Item 2 cannot be forced to live out of the house.

1. Any brother applying for a room must have less than $50 debt, including deferments, at the time room assignments are made, lest they become staggard.

@@

   a. If two or more groups of brothers wish to occupy the same room, the room will be assigned to:
      i. The group with the most brothers, not to exceed the capacity of the room; else
      i. The group of brothers with the greatest number of brothers with squatter's rights for that particular room; else
      i. The group of brothers with the lowest aggregate roster number; else
      i. The group of brothers decided by a mutually acceptable method.

>>>>

1. No alcohol is to be consumed in the house or on the chapter property.
1. No alcohol is to be stored in the house or on the chapter property except for the purposes of cooking.
   a. Alcohol stored for the purpose of cooking, determined in cases of uncertainty by a {{< var glossary.simple-majority >}} vote of chapter, may only be stored for a period of twenty-four hours.
   a. Alcohol manufactured for the sole sake of cooking (i.e. modified in such a way by the original manufacturer to make it undesirable for consuming alone or in a mixed drink), determined as above in Article VII, Section A, Item 2a, may be stored indefinitely.
1. Tobacco may not be possessed and chewed within the house or on the chapter property.
1. Illegal substances may not be possessed, stored, or used in the house or on the chapter property.
1. If a brother or their guest violates Article VII, Section A, Item 1, Article VII, Section A, Item 2, Article VII, Section A, Item 3, or Article VII, Section A, Item 4, they will be brought up for standards by the President, with sanctions not less than:
   a. First Offense – $50 fine
   a. Second Offense – $75 fine, placed on {{< var glossary.probation >}}, and becomes {{< var glossary.staggard >}}
   a. Third Offense – $100 fine and recommendation for suspension to the chapter
1. No candles will be burned inside the house or on the chapter property.
1. Article VII, Section A, Item 1, Article VII, Section A, Item 2, and Article VII, Section A, Item 3 will become null and void upon the downfall of Western Civilization.

@@

1. All active brothers are to live in the chapter house pursuant to Article V, Section 10 of the International Bylaws ({{< var acronyms.ibl >}}).
   a. The following brothers are exempt from this policy:
      i. 1st year students
      i. Commuter Students
      i. Those who are married
      i. Those who receive housing as compensation for employment (e.g. Resident Assistants)
      i. Those who are on Co-op, Study Abroad, or a similar program
      i. Those who were ineligible or exempt at the beginning of the school year\
      i. Those with a prohibitive medical condition as approved by Case Western Reserve University ({{< var acronyms.cwru >}})

@@

1. In order for a brother to move into the house, they must not be on {{< var glossary.financial-probation >}} and must not have a debt to the chapter exceeding $3000, including {{< var glossary.deferment >}}s.
   a. Brothers living in the house during the fall of any year are exempt from this stipulation for the spring semester of that year only.

@@

1. Alumni will be permitted one year after graduation or status change to live in the house without chapter approval. After that semester, the brother in question must receive a {{< var glossary.supermajority >}} vote in order to remain in the house.
   a. Alumni must be taking classes at {{< var acronyms.cwru >}} to live in the house (i.e. as a graduate student).

1. Only a spouse to a brother living in the house and taking classes at {{< var acronyms.cwru >}} may live in the house during the school year. A spouse meeting the qualifications must receive a {{< var glossary.supermajority >}} vote of the chapter to live in the house.

@@

   a. Brothers who have lived in the house during the school year for at least one semester will be allowed the option of moving out in order of pledge class from oldest to most recent, at the discretion of the Vice President.
      i. The house may not be dropped below capacity.
      i. If this method would bring the house below capacity:\
         1. Of the brothers with the highest {{< var glossary.roster-number >}} among those who wish to move out, select the number of brothers that would bring the house to a mutually acceptable method.

   a. If, after application of the method described in Article VII, Section C, Item 1a, the house is still above capacity, brothers who have lived in the most semesters in the house (excluding summer) will be forced to move out.
      i. If two or more brothers have lived in the house the same amount of time, the one with the lowest unmodified {{< var glossary.roster-number >}} will be forced to move out first.
      i. Brothers listed in Article VII, Section B, Item 2 cannot be forced to live out of the house.

1. Any brother applying for a room must have less than $50 debt, including {{< var glossary.deferment >}}s, at the time room assignments are made, lest they become {{< var glossary.staggard >}}.

@@

   a. If two or more groups of brothers wish to occupy the same room, the room will be assigned to:
      i. The group with the most brothers, not to exceed the capacity of the room; else
      i. The group of brothers with the greatest number of brothers with {{< var glossary.squatters-rights >}} for that particular room; else
      i. The group of brothers with the lowest aggregate {{< var glossary.roster-number >}}; else
      i. The group of brothers decided by a mutually acceptable method.

### 2025-09-22 src/articles/article8.qmd
Fix glossary

1. For each award that the chapter gives:
   a. Nominations will be opened prior to voting.
   a. Voting will take place after nominations have been closed.
   a. Voting will be done by show of hands.
   a. A brother may vote *No Confidence* if he is not satisfied with any of the nominees.
   a. There will be no discussion between nominations and voting.
   a. If there are less than 4 nominees, the nominee will be elected to receive the award by plurality of voting members present.
   a. Otherwise, there will be a runoff (decided by plurality) between the three nominees that received the highest counts of votes.
   a. If a plurality of votes cast are *No Confidence*, voting will end and no award will be given.

@@

1. Dream Girl Award:
   a. Will be bestowed upon the woman associated with Beta Nu Chapter who has done the most for the presently active chapter.
   a. Will be elected by the second regularly scheduled chapter meeting after initiation during the spring semester.
   a. Voting will be done by ballot in direct exception to Article VIII, Section A, Item 1b.

1. Certificate of Appreciation:
   a. May be presented to any person who has demonstrated service of extraordinary care and effort to the chapter.\
   a. Will consist of a certificate of appropriate construction and suitable wording which describes the service for which the certificate is being presented.
   a. Any brother eligible to vote may, at any chapter meeting, nominate any person.
   a. Discussion will be allowed for this award in direct exception to Article VIII, Section A, Item 1c.
   a. A nominee must receive a supermajority vote to receive this award in direct exception to Article VIII, Section A, Item 1b.
   a. The chapter may give out any number of this award.

>>>>

1. For each award that the chapter gives:
   a. Nominations will be opened prior to voting.
   a. Voting will take place after nominations have been closed.
   a. Voting will be done by show of hands.
   a. A brother may vote *No Confidence* if he is not satisfied with any of the nominees.
   a. There will be no discussion between nominations and voting.
   a. If there are less than 4 nominees, the nominee will be elected to receive the award by {{< var glossary.plurality >}} of voting members present.
   a. Otherwise, there will be a runoff (decided by {{< var glossary.plurality >}}) between the three nominees that received the highest counts of votes.
   a. If a {{< var glossary.plurality >}} of votes cast are *No Confidence*, voting will end and no award will be given.

@@

1. Dream Girl Award:
   a. Will be bestowed upon the woman associated with Beta Nu Chapter who has done the most for the presently active chapter.
   a. Will be elected by the second regularly scheduled chapter meeting after initiation during the spring semester.
   a. Voting will be done by {{< var glossary.ballot >}} in direct exception to Article VIII, Section A, Item 1b.

1. Certificate of Appreciation:
   a. May be presented to any person who has demonstrated service of extraordinary care and effort to the chapter.\
   a. Will consist of a certificate of appropriate construction and suitable wording which describes the service for which the certificate is being presented.
   a. Any brother eligible to vote may, at any chapter meeting, nominate any person.
   a. Discussion will be allowed for this award in direct exception to Article VIII, Section A, Item 1c.
   a. A nominee must receive a {{< var glossary.supermajority >}} vote to receive this award in direct exception to Article VIII, Section A, Item 1b.
   a. The chapter may give out any number of this award.
